---
title: "R Notebook"
output: html_notebook
---

```{r}
data <- data.frame(
  name=c( rep("braunhaarig",15),  
          rep("blond",5),
          rep("rothaarig",10),
          rep("schwarzhaarig",12),
          rep("bunthaarig",4))
  )
View(data)
```

```{r}
a<- sample(x = 1:2, size = 45, replace = TRUE)
a
data2 <- data.frame(
  geschlecht=c(rep("männlich",20),  
               rep("weilblich",25)),
  brille = a
  )
data2$brille
View(data2)
library(magrittr)
library(dplyr)
data1 <- data2 %>%
  mutate(brille   = factor(brille, levels = c(2, 1), labels = c("Ja - Brille", "Nein - Keine Brille")))
View(data1)
```

barplot(height, ...)

## Default S3 method:
barplot(height, width = 1, space = NULL,
        names.arg = NULL, legend.text = NULL, beside = FALSE,
        horiz = FALSE, density = NULL, angle = 45,
        col = NULL, border = par("fg"),
        main = NULL, sub = NULL, xlab = NULL, ylab = NULL,
        xlim = NULL, ylim = NULL, xpd = TRUE, log = "",
        axes = TRUE, axisnames = TRUE,
        cex.axis = par("cex.axis"), cex.names = par("cex.axis"),
        inside = TRUE, plot = TRUE, axis.lty = 0, offset = 0,
        add = FALSE, ann = !add && par("ann"), args.legend = NULL, ...)

## S3 method for class 'formula'
barplot(formula, data, subset, na.action,
        horiz = FALSE, xlab = NULL, ylab = NULL, ...)


```{r}
#name = c("braunhaarig","blond","rothaarig","schwarzhaarig","bunthaarig")
counts <- table(data$name) # Die Ausprägungen werden gezählt
counts
barplot(counts, #Infos
        main = "Säulendiagramm", #Überschrift 
        #names.arg = name,
        #beside = TRUE,
        xlab ="Haarfarben",  # x-Achse
        ylab = "Anzahl", # Y-Achse
        col = c("yellow","brown", "green", "red","black") # Farben 
        )
```

#That represents the style of axis labels. (0=parallel, 1=all horizontal, 2=all perpendicular to axis, 3=all vertical)
```{r}
counts <- table(data$name) # Die Ausprägungen werden gezählt
barplot(counts, #Infos
        main = "Balkendiagramm", #Überschrift 
        xlab ="Haarfarben",  # x-Achse
        ylab = "Anzahl", # Y-Achse
        col = c("yellow","brown", "green", "red","black"), # Farben 
        horiz=TRUE, #Drehen
        las =1 # Bezeichnung drehen
        )
```
```{r}
barplot(counts , density=c(5,10,20,30,7) , angle=c(0,45,90,11,36) , col="brown")
```



```{r}
Brille <- table(data1$geschlecht,data1$brille)
Brille

barplot(Brille,
        #beside = FALSE,
        beside = TRUE,
        col = c("red", "blue")
        )
```
```{r}
barplot(Brille, #Infos
        main = "Balkendiagramm", #Überschrift 
        xlab ="Anzahl",  # x-Achse
        ylab = "Brille", # Y-Achse
        col = c("red", "blue"), # Farben
        beside = TRUE,
        #beside = FALSE,
        horiz=TRUE, #Drehen
        las =1 # Bezeichnung drehen
        )
```

##ggplot
```{r}
library(ggplot2)
ggplot(data, aes(x=name)) +
  
  geom_bar(color= c("yellow","brown", "green", "red","black"),
           fill= c("lightskyblue1", "lightskyblue2",   
                   "lightskyblue4","lightskyblue3",
                   "lightskyblue1"))
```

```{r}

library(ggplot2)
ggplot(data, aes(x=name)) + # Daten
    geom_bar(color= c("yellow","brown", "green", "red","black"),#Farbe für die Linie
           fill= c("lightskyblue1", "lightskyblue2",    
                   "lightskyblue4","lightskyblue3",
                   "lightskyblue1"))+
coord_flip() #Drehen
```

