---
title: "Liniendiagramme"
output: html_notebook
---


##### load packages
```{r}
require(ggplot2)
require(stringi)
require(reshape2)


```



### create some dummy data:
```{r}
data = data.frame(
kw = c(12,13,14,15,16,17),
va1 = c(1500,1200,1800,1250,1400,1350),
va2 = c(2200,2200,2150,1500,800,750)
)

summary(data)


```


### Create a simple line plot with ggplot

    ggplot(data = data, aes(x =kw, y = va1))+

      geom_line()


```{r}

ggplot(data = data, aes(x =kw, y = va1))+
  
  geom_line()


```

### rename the axes:

    ggplot(data = data, aes(x =kw, y = va1))+

      geom_line()+
  
      scale_x_continuous(name = "Kalenderwoche")+
      scale_y_continuous(name = "Umsatz [€]")+
  

```{r}

ggplot(data = data, aes(x =kw, y = va1))+
  geom_line()+
  scale_x_continuous(name = "Kalenderwoche")+
  scale_y_continuous(name = "Umsatz [€]")


```

### lets change the x axis and remove week 12:

    ggplot(data = data, aes(x =kw, y = va1))+

      geom_line()+
  
      scale_x_continuous(name = "Kalenderwoche", limits = c(13,17))+
      scale_y_continuous(name = "Umsatz [€]")+
  

```{r}

ggplot(data = data, aes(x =kw, y = va1))+
  geom_line()+
  scale_x_continuous(name = "Kalenderwoche", limits = c(13,17))+
  scale_y_continuous(name = "Umsatz [€]")


```



### lets change the ugly background:

    ggplot(data = data, aes(x =kw, y = va1))+
    
      geom_line()+
      
      scale_x_continuous(name = "Kalenderwoche", limits = c(13,17))+
      scale_y_continuous(name = "Umsatz [€]")+
      
      theme_bw()



```{r}

ggplot(data = data, aes(x =kw, y = va1))+
  
  geom_line()+
  
      scale_x_continuous(name = "Kalenderwoche", limits = c(13,17))+
      scale_y_continuous(name = "Umsatz [€]")+
  
  theme_bw()


```



### still not so nice, lets change some more 


    ggplot(data = data, aes(x =kw, y = va1))+
    
      geom_line()+
      
      scale_x_continuous(name = "Kalenderwoche", limits = c(13,17))+
      scale_y_continuous(name = "Umsatz [€]")+
      
      theme_bw() + 
      theme(panel.grid.major = element_blank(),
         panel.grid.minor = element_blank(),
         panel.border = element_rect(colour = "black"),
         axis.ticks = element_line(colour = "black"),
         axis.text = element_text(colour = "black"))  


```{r}

ggplot(data = data, aes(x =kw, y = va1))+
  
  geom_line()+
  
      scale_x_continuous(name = "Kalenderwoche", limits = c(13,17))+
      scale_y_continuous(name = "Umsatz [€]")+
  
  theme_bw() + 
  theme(panel.grid.major = element_blank(),
         panel.grid.minor = element_blank(),
         panel.border = element_rect(colour = "black"),
         axis.ticks = element_line(colour = "black"),
         axis.text = element_text(colour = "black"))  



```



lets also look at the individual points: 

    ggplot(data = data, aes(x =kw, y = va1))+
  
      geom_line()+
  
      geom_point()+ 
  
      scale_x_continuous(name = "Kalenderwoche", limits = c(13,17))+
      scale_y_continuous(name = "Umsatz [€]")+
      
      theme_bw()+
      theme(panel.grid.major = element_blank(),
         panel.grid.minor = element_blank(),
         panel.border = element_rect(colour = "black"),
         axis.ticks = element_line(colour = "black"),
         axis.text = element_text(colour = "black"))  



```{r}

ggplot(data = data, aes(x =kw, y = va1))+
  
  geom_line()+
  
  geom_point()+ 
  
      scale_x_continuous(name = "Kalenderwoche", limits = c(13,17))+
      scale_y_continuous(name = "Umsatz [€]")+
  
  theme_bw()+
  theme(panel.grid.major = element_blank(),
         panel.grid.minor = element_blank(),
         panel.border = element_rect(colour = "black"),
         axis.ticks = element_line(colour = "black"),
         axis.text = element_text(colour = "black"))  



```



how about more data in on plot?


    data_long <- melt(data, id="kw")  # convert to long format


    ggplot(data = data_long, aes(x =kw, y = value, color = variable))+
  
      geom_line(aes(linetype = variable)))+
  
      geom_point(aes(shape = variable))+ 
  
      scale_x_continuous(name = "Kalenderwoche", limits = c(13,17))+
      scale_y_continuous(name = "Umsatz [€]")+
      
      theme_bw()+
      theme(panel.grid.major = element_blank(),
            panel.grid.minor = element_blank(),
            panel.border = element_rect(colour = "black"),
            axis.ticks = element_line(colour = "black"),
            axis.text = element_text(colour = "black"))  



```{r}

print(data)


```

stack columns:

    data_long <- melt(data[,1:3], id="kw")  # convert to long format

```{r}

data_long <- melt(data[,1:3], id="kw")  # convert to long format


print(data_long)

```

```{r}

ggplot(data = data_long, aes(x =kw, y = value, color = variable))+
  
  geom_line(aes(linetype = variable))+
  
  geom_point(aes(shape = variable))+ 
  
      scale_x_continuous(name = "Kalenderwoche", limits = c(13,17))+
      scale_y_continuous(name = "Umsatz [€]")+
  
  theme_bw()+
  theme(panel.grid.major = element_blank(),
         panel.grid.minor = element_blank(),
         panel.border = element_rect(colour = "black"),
         axis.ticks = element_line(colour = "black"),
         axis.text = element_text(colour = "black"))  

```



and have a log_10 on the y axis: 

    data_long <- melt(data, id="kw")  # convert to long format


    ggplot(data = data_long, aes(x =kw, y = value, color = variable))+
  
      geom_line(aes(linetype = variable)))+
  
      geom_point(aes(shape = variable))+ 
  
      scale_x_continuous(name = "Kalenderwoche", limits = c(13,17))+
      scale_y_log10(name = "Umsatz [€]", limits =c(100,10000))+
      
      theme_bw()+
      theme(panel.grid.major = element_blank(),
            panel.grid.minor = element_blank(),
            panel.border = element_rect(colour = "black"),
            axis.ticks = element_line(colour = "black"),
            axis.text = element_text(colour = "black"))  



```{r}

data_long <- melt(data[,1:3], id="kw")  # convert to long format


ggplot(data = data_long, aes(x =kw, y = value, color = variable))+
  
  geom_line(aes(linetype = variable))+
  
  geom_point(aes(shape = variable))+ 
  
      scale_x_continuous(name = "Kalenderwoche", limits = c(13,17))+
      scale_y_log10(name = "Umsatz [€]", limits =c(100,10000))+
  
  theme_bw()+
  theme(panel.grid.major = element_blank(),
         panel.grid.minor = element_blank(),
         panel.border = element_rect(colour = "black"),
         axis.ticks = element_line(colour = "black"),
         axis.text = element_text(colour = "black"))  

```


put the legend inside of the plot? 

    data_long <- melt(data, id="kw")  # convert to long format


    ggplot(data = data_long, aes(x =kw, y = value, color = variable))+
  
      geom_line(aes(linetype = variable)))+
  
      geom_point(aes(shape = variable))+ 
  
      scale_x_continuous(name = "Kalenderwoche", limits = c(13,17))+
      scale_y_log10(name = "Umsatz [€]", limits =c(100,10000))+
      
      theme_bw()+
      theme(panel.grid.major = element_blank(),
            panel.grid.minor = element_blank(),
            panel.border = element_rect(colour = "black"),
            axis.ticks = element_line(colour = "black"),
            axis.text = element_text(colour = "black"),
            legend.position = c(0.9, 0.85))  



```{r}

data_long <- melt(data[,1:3], id="kw")  # convert to long format


ggplot(data = data_long, aes(x =kw, y = value, color = variable))+
  
  geom_line(aes(linetype = variable))+
  
  geom_point(aes(shape = variable))+ 
  
      scale_x_continuous(name = "Kalenderwoche", limits = c(13,17))+
      scale_y_log10(name = "Umsatz [€]", limits =c(100,10000))+
  
  theme_bw()+
  theme(panel.grid.major = element_blank(),
         panel.grid.minor = element_blank(),
         panel.border = element_rect(colour = "black"),
         axis.ticks = element_line(colour = "black"),
         axis.text = element_text(colour = "black"),
         legend.position = c(0.9, 0.85))

```

